### 2023-05-07 thesis/chapters/02-analysis-A-CdM.tex
Summarize articles of high relevance for feature engineering section

Rotating machine disorders do exhibit frequency signatures at various ranges in the frequency spectrum with supplementary symptoms carried in phase. Most of the occurring faults can be tied to the main rotational speed of the component under investigation (Fig.~\ref{fig:machinery-vibrations})~\cite{davies_handbook_2012}. Imbalance, misalignment, and looseness normally appear at frequencies up to 300 Hz. These low-frequency faults are associated with the movement of the shaft and primarily coincide with revolution speed and its harmonics. Bearing and gearbox defects in the late stages of development, show up in the range between 300 Hz to 1 kHz. Higher frequencies measured traditionally to a limit of 10 kHz help notice the deficiencies in bearings even sooner~\cite{torres_automatic_2022}.

@@

Because of inherent tolerances in machine manufacturing and assembly, the rotational frequency always manifests itself, even in baseline signature~\cite{davies_handbook_2012, noauthor_iso_2002}. In the most likely scenario, some faults appear as compared to rotational frequency solely in\textbf{synchronous, subsynchronous, or non-synchronous components}. The defects can occur also in a predictable combination of the ones mentioned. Other common patterns experts look for are modulation sidebands typical for bearings and gears extractable with cepstrum analysis~\cite{ziaran_technicka_2013}. Therefore procedure relying on elimination narrows down unrelated causes effectively.

@@

The condition monitoring programme is run according to a flowchart adapted from one designed in the standard specifically to best benefit the plant. Those steps can be summarized as follows ~\cite{noauthor_iso_2002}:
\begin{enumerate}
\itemsep0pt
\item Review machinery history and establish failure modes.
\item When vibration monitoring is not applicable check for other condition monitoring techniques or resort to preventive maintenance.
\item Select monitoring points and take preliminary vibration measurements.
\item Select vibration monitoring techniques: broadband, frequency analysis, or special techniques, and set parameters of measurement units.
\item Take baseline measurements.
\item Change levels that would warrant investigation.
\item Carry out routine condition monitoring.
\item If an alarm was exceeded, notify appropriate personnel to review data and trends, perform diagnostic evaluation, and repair as necessary. In case a new baseline is needed continue in the step of taking baseline measurements.
\item Shut down the machine when the trip level is exceeded. Then proceed the same as after the alarm trigger.
\end{enumerate}

>>>>

Rotating machine disorders do exhibit frequency signatures at various ranges in the frequency spectrum with supplementary symptoms carried in phase. Most of the occurring faults can be tied to the main rotational speed of the component under investigation (Fig.~\ref{fig:machinery-vibrations})~\cite{davies_handbook_2012}. Imbalance, misalignment, and looseness normally appear at frequencies up to 300 Hz. These low-frequency faults are associated with the movement of the shaft and primarily coincide with revolution speed and its harmonics. Bearing and gearbox defects in the late stages of development, show up in the range between 300 Hz to 1 kHz. Higher frequencies, measured traditionally to a limit of 10 kHz, help notice the deficiencies in bearings even sooner~\cite{torres_automatic_2022}.

@@

Because of inherent tolerances in machine manufacturing and assembly, the rotational frequency always manifests itself, even in baseline signature~\cite{davies_handbook_2012, noauthor_iso_2002}. In the most likely scenario, some faults appear as compared to rotational frequency solely in \textbf{synchronous, subsynchronous, or non-synchronous components}. The defects can occur also in a predictable combination of the ones mentioned. Other common patterns experts look for are modulation sidebands typical for bearings and gears extractable with cepstrum analysis~\cite{ziaran_technicka_2013}. Therefore procedure relying on elimination narrows down unrelated causes effectively.

@@

The condition monitoring programme is run according to a flowchart adapted from one designed in the standard specifically to best benefit the plant. Those steps can be summarized as follows~\cite{noauthor_iso_2002}:
\begin{enumerate}
\itemsep0pt
\item Review machinery history and establish failure modes.
\item When vibration monitoring is not applicable check for other condition monitoring techniques or resort to preventive maintenance.
\item Select monitoring points and take preliminary vibration measurements.
\item Select vibration monitoring techniques: broadband, frequency analysis, or special techniques, and set parameters of measurement units.
\item Take baseline measurements.
\item Change levels that would warrant investigation.
\item Carry out routine condition monitoring.
\item If an alarm was exceeded, notify appropriate personnel to review data and trends, perform diagnostic evaluation, and repair as necessary. In case a new baseline is needed continue in the step of taking baseline measurements.
\item Shut down the machine when the trip level is exceeded. Then proceed the same as after the alarm trigger.
\end{enumerate}

### 2023-05-07 thesis/chapters/02-analysis-B-features.tex
Summarize articles of high relevance for feature engineering section

\subsection{Feature extraction}
% Feature Engineering for Machine Learning
\cite{zheng_feature_2018}
% Feature Engineering and Selection: A Practical Approach for Predictive Models
\cite{johnson_feature_2019}
% A New Statistical Features Based Approach for Bearing Fault Diagnosis Using Vibration Signals
\cite{altaf_new_2022}
% A Novel Online Machine Learning Approach for Real-Time Condition Monitoring of Rotating Machines
\cite{mostafavi_novel_2021}
% Fault Detection of Bearing: An Unsupervised Machine Learning Approach Exploiting Feature Extraction and Dimensionality Reduction
\cite{brito_fault_2021}
% A large setof audio features for sound description
\cite{peeters_large_2004}
% Research on online intelligent monitoring system of band saw blade wear status based on multi‑feature fusion of acoustic emission signals
\cite{zhuo_research_2022}
% Early Detection of Imbalance in Load and Machine In Front Load Washing Machines by Monitoring Drum Movement
\cite{mohammadi_early_2020}
% A Data Mining based Approach for Electric Motor Anomaly Detection Applied on Vibration Data
\cite{egaji_data_2020}
% Condition Monitoring with Vibration Signals
\cite{nandi_condition_2019}

@@

\paragraph{Statistical measures}
\begin{itemize}
\item Standard Deviation
\item Max. amplitude
\item RMS amplitude
\item Skewness
\item Kurtosis \\
---
\item Spectral centroid
\item RMS frequency
\item Root variance frequency
\item Spectral kurtosis / Fast kurtogram
\item Harmonics (peaks)
	% Comparative Study of Various CFAR Algorithms for Non-Homogenous Environments
	\cite{hatem_comparative_2018}
	% Multi-Scale Peak and Trough Detection Optimised for Periodic and Quasi-Periodic Neuroscience Data
	\cite{bishop_multi-scale_2018}
	% Non-Parametric Local Maxima and Minima Finder with Filtering Techniques for Bioprocess
	\cite{adikaram_non-parametric_2016}
	% Identification of harmonics and sidebands in a finite set of spectral components
	\cite{gerber_identification_2013}
	% Evaluation of Threshold-Based Algorithms for Detection of Spectral Peaks in Audio
	\cite{nunes_evaluation_2007}
	% Statistical techniques to select detection thresholds for peak signals in ice-core data
	\cite{karlof_statistical_2005}
\item Spectral Envelope
\item Harmonic spectral deviation \\
---
\item Energy
\item Spectral negentropy
	% Spectral negentropy and kurtogram performance comparison for bearing fault diagnosis
	\cite{avoci_spectral_2020}
\item TKEO - Teager-Kaiser energy operator
	%Application of Teager–Kaiser Energy Operator in the Early Fault Diagnosis of Rolling Bearings
	\cite{shi_application_2022}
\end{itemize}

\paragraph{Wavelet signal decomposition}
%Matching pursuit algorithm optimalization problem
\cite{song_mfbd_2021}
\begin{itemize}
\item FFT - Short Time Fourier Transform with Hamming window and Welch averaging
	% \cite{oulmane_automatic_2015}

\item CWT-SST - Synchrosqueezing Wavelet Transform
	% The fast continuous wavelet transformation (fCWT) for real-time, high-quality, noise-resistant time–frequency analysis
	\cite{arts_fast_2022}
	% A Concentrated Time–Frequency Analysis Tool for Bearing Fault Diagnosis
	\cite{yu_concentrated_2020}
	% Applications of the synchrosqueezing transform in seismic time-frequency analysis
	\cite{herrera_applications_2014}

\item WPD - Wavelet Packet Decomposition  - to approximation and detail coef. (Fejer-Korovkin wavelet)
	% Wavelet Packet Feature Extraction for Vibration Monitoring
	\cite{yen_wavelet_2000}
	% A wavelet approach to dimension reduction and classiﬁcation of hyperspectral data
	\cite{wickmann_wavelet_2007}

@@

\subsection{Feature transformation}
\cite{zheng_feature_2018}
\begin{itemize}
\item Normalization (min-max, standardize)
\item Log transformation (Box-Cox Transform) to normal distribution
\item Principal Component Analysis (PCA)
\end{itemize}

\subsection{Feature selection}
Subset generation p.193
Subset evaluation
Stopping criteria
Validation

\cite{nandi_condition_2019} p.192
Filter method - SelectKBest  in evaluation phase
\begin{itemize}
\item Variance Threshold
\item Pearson correlation
\item ANOVA F-value
\item Mutal information
\item Fisher score
\item Spectral feature selection algorithm (SPEC)
\end{itemize}

>>>>

\subsection{Feature extraction}
% Feature Engineering for Machine Learning
\cite{zheng_feature_2018}
% Feature Engineering and Selection: A Practical Approach for Predictive Models
\cite{johnson_feature_2019}

% A Novel Online Machine Learning Approach for Real-Time Condition Monitoring of Rotating Machines
% - list of features
\cite{mostafavi_novel_2021}

% A New Statistical Features Based Approach for Bearing Fault Diagnosis Using Vibration Signals
% - knn with manhalobis distance
% - select features manually as oposed to CNN and RNN
\cite{altaf_new_2022}
$$X_{rms} = \sqrt{\frac{1}{N} \sum_{i=1}^{N}{x_i^2}}$$  % rms
$$X_{cf} = \frac{\max(|x_i|)}{X_{rms}}$$  % crest factor

$$ $$% standard deviation
$$X_{kv} = \frac{1}{N}  \sum_{i=1}^{N}{\frac{x_i - \bar{x}}{\sigma}} $$ % kurtosis

% Fault Detection of Bearing: An Unsupervised Machine Learning Approach Exploiting Feature Extraction and Dimensionality Reduction
% - Time domain: mean, standard deviation, rms (root mean square), peak value, peak-topeak value, shape indicator, skewness, kurtosis, crest factor, clearance indicator, etc. (ii) Frequency domain: mean frequency, central frequency, energy in frequency bands, etc. (iii) Time-frequency domain: entropy are usually extracted by Wavelet Transform, Wavelet Packet Transform, and empirical model decomposition.
\cite{brito_fault_2021}

FFT - Short Time Fourier Transform with Hamming window and Welch averaging
	% \cite{oulmane_automatic_2015}

% A large setof audio features for sound description
\cite{peeters_large_2004}
% Research on online intelligent monitoring system of band saw blade wear status based on multi‑feature fusion of acoustic emission signals
\cite{zhuo_research_2022}
% Early Detection of Imbalance in Load and Machine In Front Load Washing Machines by Monitoring Drum Movement
\cite{mohammadi_early_2020}
% A Data Mining based Approach for Electric Motor Anomaly Detection Applied on Vibration Data
\cite{egaji_data_2020}
% Condition Monitoring with Vibration Signals
\cite{nandi_condition_2019}

@@

\paragraph{Statistical measures}
\begin{itemize}
\item Standard Deviation
\item Max. amplitude
\item RMS amplitude
\item Skewness
\item Kurtosis \\
---
\item Spectral centroid
\item RMS frequency
\item Root variance frequency
\item Spectral kurtosis / Fast kurtogram
\item Harmonics (peaks)
	% Multi-Scale Peak and Trough Detection Optimised for Periodic and Quasi-Periodic Neuroscience Data
	\cite{bishop_multi-scale_2018}
	% Non-Parametric Local Maxima and Minima Finder with Filtering Techniques for Bioprocess
	\cite{adikaram_non-parametric_2016}
	% Identification of harmonics and sidebands in a finite set of spectral components
	\cite{gerber_identification_2013}
	% Evaluation of Threshold-Based Algorithms for Detection of Spectral Peaks in Audio
	\cite{nunes_evaluation_2007}
\item Spectral Envelope
\item Harmonic spectral deviation \\
---
\item Energy
\item Spectral negentropy
	% Spectral negentropy and kurtogram performance comparison for bearing fault diagnosis
	\cite{avoci_spectral_2020}
\item TKEO - Teager-Kaiser energy operator
	%Application of Teager–Kaiser Energy Operator in the Early Fault Diagnosis of Rolling Bearings
	\cite{shi_application_2022}
\end{itemize}

\paragraph{Wavelet signal decompositions}

\begin{itemize}
\item CWT-SST - Synchrosqueezing Wavelet Transform
	% The fast continuous wavelet transformation (fCWT) for real-time, high-quality, noise-resistant time–frequency analysis
	\cite{arts_fast_2022}
	% A Concentrated Time–Frequency Analysis Tool for Bearing Fault Diagnosis
	\cite{yu_concentrated_2020}
	% Applications of the synchrosqueezing transform in seismic time-frequency analysis
	\cite{herrera_applications_2014}

\item WPD - Wavelet Packet Decomposition  - to approximation and detail coef. (Fejer-Korovkin wavelet)
	% Wavelet Packet Feature Extraction for Vibration Monitoring
	\cite{yen_wavelet_2000}
	% A wavelet approach to dimension reduction and classiﬁcation of hyperspectral data
	\cite{wickmann_wavelet_2007}
	% The MFBD: a novel weak features extraction method for rotating machinery
	\cite{song_mfbd_2021}

@@

\subsection{Feature transformation}
\cite{zheng_feature_2018}
\begin{itemize}
\item Normalization (min-max, standardize)
\item Log transformation (Box-Cox Transform) to normal distribution
\item Principal Component Analysis (PCA)  % \cite{brito_fault_2021}
\end{itemize}

\subsection{Feature selection}
Subset generation % p.193
Subset evaluation
Stopping criteria
Validation

\cite{nandi_condition_2019} % p.192
Filter method - SelectKBest  in evaluation phase
\begin{itemize}
\item Variance Threshold
\item Pearson correlation
\item ANOVA F-value
\item Mutal information
\item Fisher score
\item Spectral feature selection algorithm (SPEC)
\end{itemize}
